Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-23 tex/main/manuscript.tex
过一遍引言第二节的第二段

\subsection*{Development Traps}
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}). Like social-ecological systems and other complex systems, coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, or collapse emerged because of structural mismatches. A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems. Thus, it is crucial to distinguish major development traps based on the transition framework of water utilization regimes.

@@

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies from watersheds around the world, big river basins often face a resource trap at the beginning of their development, while highly developed ones often face a structural trap.
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
For the Yellow River Basin, after the successive expansion of agriculture and industrial services during the P1 and P2 phases, the utilization rate of surface water resources has reached 80\% of the natural runoff, far exceeding the internationally recognized threshold of 40\%. Although water management measures in P1 (construction of numerous reservoirs) mitigated the pressure on water resources due to accelerated development, the pressure on water resources rebounded rapidly during P2, when the number of new reservoirs declined significantly. These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, and the Yellow River basin had been in a notable resource trap.
% 资源困局可能普遍存在
In any case, the xxx and xxx basins have a development history similar to that of the Yellow River, 
suggesting that resource distress may be widespread in the early stages of the transition.

>>>>

\subsection*{Development Traps}
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}). 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the gradual pressure on resources or because of structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Thus, our transition framework can identify regime shifts of water utilization, which can help to predict possible development traps.

@@

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies around the world, big river basins often face resource traps at the beginning of their developments, while highly developed ones often face structural traps.
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
During P1 and P2 (refers from natural cycle to the local cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift. The resource trap is revealed at this point, with severe runoff outages and groundwater depletion of the Yellow River from P2 onwards (supplementary Fig. S8).
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to local cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
